---
title: "Using the fars Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the fars Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fars)
```

## make_filename  
Use make_filename to build the filename for raw data file:
```{r make_filename}
make_filename(2013)
```

## fars_read   
Use fars_read to read in the complete data from a given year. By default, this function reads data provided with the package in the directory inst/extdata. If the parameter package_file is set to FALSE, this function will read files in the working directory.
```{r read_file}
data <- fars_read(make_filename(2013),package_file = TRUE)
str(data)
```

## fars_read_years  
Use fars_read_years to read in multiple years, and return a list of tibbles
```{r read_years}
data <- fars_read_years(c(2013,2014,2015))
head(data)
```

## fars_summarize_years  
Use fars_read_years to read in multiple years, and return a tibble with the number
of incidents broken down by month and year
```{r fars_summarize_years}
data <- fars_summarize_years(c(2013,2014,2015))
head(data)
```

## fars_map_state  
Use fars_map_state to read in a single year, and plot the incidents
on a map of the state by latitude and longitude coordinates
```{r fars_map_state}
data <- fars_map_state(1,2015)
```
